A community-maintained standard library of population genetic models

### 2020-04-29 popSimManu.tex
added text about masking

Following simulation, low-recombination portions of chromosomes were masked
from the analysis in a manner that reflects the ``accessible" subset of sites
used in empirical population genomic studies \citep[e.g.,][]{danecek20111000,langley2012genomic}.
Specifically we masked all regions of \SI{1}{cM} or greater in the lowest 5th percentile of the empirical
distribution of recombination, regions which are nearly uniformly absent for
empirical analysis.

>>>>

Following simulation, low-recombination portions of chromosomes were masked
from the analysis in a manner that reflects the ``accessible" subset of sites
used in empirical population genomic studies \citep[e.g.,][]{danecek20111000,langley2012genomic}.
Specifically we masked all regions of \SI{1}{cM} or greater in the lowest 5th percentile of the empirical
distribution of recombination, regions which are nearly uniformly absent for
empirical analysis. This approach to masking was chosen to prevent marginal trees with low or no recombination 
from biasing the comparisons of demographic inference methods. It should be noted that masking is not implemented 
within \texttt{stdpopsim} proper; tree sequences generated by \texttt{stdpopsim} are always raw and unmasked. 
This allows users the flexibility to implement masking approaches that are specific to their needs 
for downstream analysis.
